Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-29 scripts/MouseSexDiffApril20_2020.Rmd
space out fig S2

```{r Fig4}
Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(9, 9), labels = c("A", "B"))
Fig4
```

@@

FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
FigS1
#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
```

@@

This figure is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison. The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance). Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
```{r FigS2, fig.height = 8, fig.width = 7}
library(ggpubr)
FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1, 1)
)

@@

# end combination Figure 5
FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.4, 2.1, 2.1, 2), labels = c("A", " ", "B", " "))
FigS2
#ggsave("FigS2_Bias.pdf", plot = FigS2, width = 7, height = 8)
```

>>>>

```{r Fig4}
Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
Fig4
```

@@

FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
FigS1
#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
```

@@

This figure is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison. The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance). Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
```{r FigS2, fig.height = 10, fig.width = 8}
library(ggpubr)
FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2)
)

@@

# end combination Figure 5
FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
FigS2
```
